### 2017-11-14 related.tex
related

In our problem, there is not only gaps in the observation (packets missed by the
sniffer), but also uncertainty regarding observed events, which lies in whether
a packet in the sniffer trace was received by its destination device. This
unique challenge makes it infeasible to directly apply the HMM-based approaches
proposed in~\cite{stoller2011runtime}.
Besides, there are several advantages of our proposed augmented transition
approach. First, the automatically augmented state machine precisely encodes the
protocol specification and the uncertainty. This is intuitive to design and
natural for
reporting the evidence for a trace being successful. We do not require a user
to specify the number of states of the underlying HMM, or accurately provide
underlying probabilities. Second, we use timed automata to monitor the timing
constraints which are common in wireless protocols. It may be non-trivial to
encode such timing information in HMM. Finally, we can exploit domain knowledge
to devise effective pruning heuristics to rule out unlikely sequences during the
exhaustive search.

\textbf{Edit Distance.} The closet work to ours is the Edit distance based approach
to monitor STL properties of real time systems~\cite{jakvsic2016quantitative}.

>>>>

In our problem, there are not only gaps in the observation (packets missed by the
sniffer), but also uncertainty regarding observed events, which lies in whether
a packet in the sniffer trace was received by its destination device. This
unique challenge makes it infeasible to directly apply the HMM-based approaches
proposed in~\cite{stoller2011runtime}.
Besides, there are several advantages of our proposed augmented transition
approach. First, the automatically augmented state machine precisely encodes the
protocol specification and the uncertainty. This is intuitive to design and
natural for
reporting the evidence for a trace being successful. We do not require a user
to specify the number of states of the underlying HMM, or accurately provide
underlying probabilities. Second, we use timed automata to monitor the timing
constraints which are common in wireless protocols. It may be non-trivial to
encode such timing information in HMM. Finally, we can exploit domain knowledge
to devise effective pruning heuristics to rule out unlikely sequences during the
exhaustive search.

\textbf{Edit Distance.} The closet work to ours
is~\cite{jakvsic2016quantitative}, which uses the weighted edit distance to
measure the robustness between digitized Cyber-Physical System (CPS) signals and
STL specifications. The automaton of verifying STL properties is first
translated into weighted edit automaton, which explicitly handles substitution,
insertion and deletion by augmenting the original automaton with transitions and
associating to them the appropriate weight function. An observed signal sequence
is then input into the weighted edit automaton to compute the weighted edit
distance between the observation and the specification.

We share the same spirit with~\cite{jakvsic2016quantitative} in that we also
explicitly handle the sniffer trace uncertainty using the augmented transitions.
However, there is no need for substitution in our application scenario, as the
sniffer can only either receive or miss a packet, but can not mis-interpret
packets. In addition, ~\cite{jakvsic2016quantitative} only considers real value
observations, and relies on this restriction to define the edit distance for
insertion transitions. The approach can not be directly applied in our case
since we need to deal with compound observations (packets).
